Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-28 manuscript.Rmd
Update tweet count

# Method
## Materials
### Tweet Corpus
The corpus of tweets used included 8,084,644 Syrian tweets occurring between March 1, 2012 and June 15, 2012. A server malfunction during data collection resulted in missing data from March 12, 2012 to March 29, 2012. For the current analyses, the data were truncated to remove missing data, making the final dataset from March 30, 2012 to June 15, 2012 (n = 78). The tweet corpus was scraped from Twitter by [insert search parameters here].

>>>>

# Method
## Materials
### Tweet Corpus

```{r tweet-count, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# read in social cohesion data
cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")

The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets occurring between March 30, 2012 and June 15, 2012. The tweet corpus was scraped from Twitter by [insert search parameters here].

### 2020-05-28 manuscript.tex
Update tweet count

The corpus of tweets used included 8,084,644 Syrian tweets occurring between March 1, 2012 and June 15, 2012. A server malfunction during data collection resulted in missing data from March 12, 2012 to March 29, 2012. For the current analyses, the data were truncated to remove missing data, making the final dataset from March 30, 2012 to June 15, 2012 (n = 78). The tweet corpus was scraped from Twitter by {[}insert search parameters here{]}.

>>>>

The corpus of tweets used included 697428 Syrian tweets occurring between March 30, 2012 and June 15, 2012. The tweet corpus was scraped from Twitter by {[}insert search parameters here{]}.
